My title

### 2024-11-04 paper/paper.qmd
model description

This is Model 1, follows Bayesian Model

@@

*define each vairable here*
```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \beta_0 + \beta_1 \times \mbox{State}_i + \beta_2 \times \mbox{Days Since First Poll}_i + \beta_3 \times \mbox{Pollster}_i \\
\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
\beta_3 &\sim \mbox{Exponential}(1)
\end{align}
```

@@

bayesian_model <- stan_glmer(
  formula = model,
  data = harrisdata,
  family = binomial(link = "logit"),
  prior = priors,
  prior_intercept = priors,
  seed = 123,
  cores = 4,
  adapt_delta = 0.95)
```

>>>>

@@

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \beta_0 + \beta_1 \times \mbox{State}_i + \beta_2 \times \mbox{Pollster}_i + \beta_3 \times \mbox{Days since first poll}_i\\
\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
\beta_3 &\sim \mbox{Exponential}(1)
\end{align}
```

We used the `stan_glmer` function from `rstanarm` package to create a Bayesian regression model with a Normal distribution. The dependent variable in the proportion of respondent who support Kamala Harris, and our model aims to predict Harris' support based on several importnat factors, modeled by:

@@

bayesian_model <- stan_glmer(
  formula = model,
  data = harrisdata,
  family = binomial(link = "logit"),
  prior = priors,
  prior_intercept = priors,
  # weights = harrisdata$numeric_grade,
  seed = 123,
  cores = 4,
  adapt_delta = 0.95)
```

where:

- $y_i$ is the dependent variable, represneting the proportion of respondents who support Harris
- $\beta_0$ is the intercept term, representing the expected proportion of $y_i$ when all other predictors are set to zero.
- $\beta_1$ corresponds to the `state` choosing one of seven states,
- $\beta_2$ corresponds to the `pollster`,
- $\beta_3$ is the value representing number of days since the first poll.

All variables follow the normal distribution with a mean of 0 and a standard deviation of 2.5.
